---
title: "Final Presentation"
author: "Author: Ali Lmalki"
date: "`r format(Sys.time(), '%B %d, %Y @ %I:%M %p')`"
output: ioslides_presentation
---

```{r global_options, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  comment = NA
)
```

## Packages Used

I used tidyverse for data manipulation and plotting.

```{r, echo = TRUE}
library(tidyverse)
```


## Olympic Games Dataset

I compiled my dataset from [Kaggle](https://www.kaggle.com/datasets).

The dataset was last updated March 14, 2022, so some of the values may have changed between that date and now. 

**Variables in the Dataset:**

* `Name`: Name of the athlete
* `Sex`: Male (M) or Female (F)
* `Age`: Age of the athlete
* `Team` Country from which the athlete plays for
* `Games`: The game in which the athlete participated in
* `Year`: The year in which the athlete participated in
* `Season`: The year in which the athlete participated in
* `Sport`: The sport played by the athlete
* `Medal`: 0 - No Medal 1 - Bronze Medal 2 - Silver Medal 3 - Gold Medal


```{r}
data <- read_csv("data/olympic_games.csv")
```


##

```{r, fig.align = "center", fig.width = 7.5}
data %>%
filter(Medal > 0) %>%
group_by(Team)%>%
count()%>%
rename(All_time_Medals = n)%>%
arrange(All_time_Medals)%>%
tail(10)%>%
ggplot()+
geom_col(aes(y= reorder(Team,All_time_Medals),fill=Team,x=All_time_Medals)) +
  labs(title = "Top 10 countries with the Maximum number of medals", x = "Number of Medals", y = "Name of the Country")
```

This graph shows the top 10 countries with the highest number of medals. The United States is on top of the list followed by the Soviet Union.


##

```{r, fig.align = "center", fig.width = 9}
data %>%
filter(Medal > 0, Team == "Sweden") %>%
group_by(Year)%>%
count()%>%
rename(Total = n) %>%
ggplot() +
geom_line(aes(x=Year,y = Total)) +
labs(title = "Sweden Performance In Olympics over Time",
    x= "Year",
    y="Number of medals",
    caption = "Data Source: Kaggle")
```

This graph depicts the evolution of Swedish atheles performance in the olympics. We can notice a decrease on their performance over the years.


